Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-12 surfaces-write-up/surface-write-up.tex
minor edit to use Z_{\geq 0}^2

Now we show that no further generators are necessary. As done in
the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
{dorney:canonical}, each lattice point $(d, c) \in \bz^2$ such that
$c \leq d \alpha$ is a nonnegative linear combination of $\vec{x}_i$
and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in \bz^2$.
Consequently, any element $\frac{u^{d} x^{\vec{v}}} {x_k^{c}} \in
R_D$ is expressible as
\begin{align*}
	\frac{u^{d} x^{\vec{v}}} {x_k^{c}} = \frac{u^{d_i} x^{\vec{w}}}
	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}
\end{align*}

>>>>

Now we show that no further generators are necessary. As done in
the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
{dorney:canonical}, each lattice point $(d, c) \in \bz_{\geq 0}^2$
such that $c \leq d \alpha$ is a nonnegative linear combination of
$\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
\bz^2$. Consequently, any element $\frac{u^{d} x^{\vec{v}}}
{x_k^{c}} \in R_D$ is expressible as
\begin{align*}
	\frac{u^{d} x^{\vec{v}}} {x_k^{c}} = \frac{u^{d_i} x^{\vec{w}}}
	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}
\end{align*}
